miniKanren with fair search strategies

### 2019-05-05 Paper/paper.tex
simpl def of state

In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
Before going further into fairness, we would like to give a short review about 
state, search space, and goal, because fairness is defined in terms of them. 
Each \emph{state} records a way how some relations can be satisfied. Every 
answer given by miniKanren corresponds to a state. In our case, the state is 
just a substitution associating logic variables with terms. In more expressive 
miniKanrens (e.g. miniKanren with with symbolic constraints 
\citep{hemann2017framework}), states can include more information. A 
\emph{search space} is a collection of states. And a \emph{goal} is a function 
from a state to a search space. Goals check their input states and outputs 
possibly extended states. A goal might fail for some inputs, in which case the 
output search space would be empty.

>>>>

In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
Before going further into fairness, we would like to give a short review about 
state, search space, and goal, because fairness is defined in terms of them. 
A \emph{state} is a collection of constraints. Every answer given by 
miniKanren corresponds to a state. A \emph{search space} is a collection of 
states. And a \emph{goal} is a function from a state to a search space. Goals 
check their input states and outputs possibly extended states. A goal might fail 
for some inputs, in which case the output search space would be empty.
